### 2015-10-10 README.Rmd
updated readme again

```{r}
# Note that your custom data frame of company names and tickers must have the column name "ticker" for the column of tickers.

@@

## Renders raw data in a format usable by other functions in this package and also dramatically improves readability.

@@

## Retrieves stock price data from Google Finance for listed companies for the past two years. Also saves data from the S&P 500, retrieved from Yahoo Finance.

>>>>

```{r}
## Note that your custom data frame of company names and tickers must have the column name 
## "ticker" for the column of tickers.

@@

## Renders raw data in a format usable by other functions in this package 
## and also dramatically improves readability.

@@

## Retrieves stock price data from Google Finance for listed companies for the past two years. 
## Also saves data from the S&P 500, retrieved from Yahoo Finance.
